\LARGE \bf ``Those who can't do, teach'': a Teachable Robotic Agent for Children Learning Handwriting

### 2014-09-29 main.tex
Polishing

Presented is a robotic partner which children can teach handwriting. It is
hypothesised that such a system could not just engage an unmotivated student,
but could also present the opportunity for children to experience the typical
benefits encountered during human-led handwriting interventions, such as motor
mimicry. Moreover, this system allows for exploring the potential for the
\emph{learning by teaching} paradigm to be employed in the interaction, so as to
stimulate meta-cognition, empathy and increased self-esteem in the child user.

@@

If there is correlation between the points in the observations, there will be
eigenvalues of the covariance matrix which are close to zero. As such, removing
the associated eigenvectors from ${\bf \Phi}$ allows for dimensionality
reduction with minimal impact. Indeed, the amount of variance in the dataset
that is explained by each eigenvector ${\bf v}_i$ is $\sqrt{\lambda_i}$, and
therefore the proportion of the variance explained by each dimension/eigenvector
is as shown in (\ref{eq:proportionVar}).

\begin{equation}\label{eq:proportionVar}
\%var_i = \frac{\sqrt{\lambda_i}}{\sum_{i=1}^{N}\sqrt{\lambda_i}}\times 100\%
\end{equation}

@@

Figure \ref{fig:demonstrationShapes2} illustrates the response of the system to
demonstrations from a child for the letter `s' using a learning rate of
$\alpha=1/2$.

@@

\begin{figure}[thpb]
     \begin{center}
        %\subfigure{
        %    \includegraphics[width=0.4\textwidth]{figures/naoWriting1.png}
        %}%
        \subfigure{
            \includegraphics[width=0.8\linewidth]{figures/naoWriting2.png}
        }%
%
    \end{center}
    \caption{A demonstration of the robot simulating the writing of a word with
    its finger. The motion of the robot is synchronised with the display of the
    tablet, communicating over ROS.\protect\footnotemark}%

@@

As noted in the introduction, a conclusion drawn in~\cite{Hoy2011} is that any 
handwriting intervention studies considered in the systematic review which involved 
fewer than two practice sessions per week and fewer than a total of 20 practice 
sessions, including homework, were not found to demonstrate effective results. This 
highlights the necessity to engage students in an interaction which will be sustainable
 over the long-term if we wish to move towards using the proposed system to answer 
research questions which involve the measurement of learning gains to gauge effects. 
Several challenges are raised in developing such long-term capabilities for the system,
 from both technical and socialogical points of view. %not sure this makes sense

@@

In the current system, the robot can ask questions and prompt participants, but it 
cannot engage in discussions with the participants. It is clear that work is necessary 
to develop the conversational agent in the interaction so that the presence of an 
experimenter is not required for a captivating engagement. While there is the 
possiblity to focus the interaction design on group-based interaction with the robot 
in order to alleviate the necessity of a conversational agent, there is reason to 
suggest that constructing such a social interaction is not a trivial task. Anectodes 
from the preliminary studies have shown that some children may criticise another's 
demonstrations to the robot, which may or may not be as damaging to a child's 
self-efficacy as when they are criticised in a typical educational context. In addition,
on occassions where a pair of children came to teach the robot different styles of a 
particular letter, they did not discuss with each other their different writing styles 
and the effect on the teaching efficiency. This may suggest that a social context in 
which verbalising opinions about differences is encouraged is necessary to get children 
to cooperate in teaching the robot.  
%- "Would have problems with the 'n'" - (8) projecting human learning characteristics.
%- awkward silence, speaking over the top of the robot to talk to experimenter....
%- Children saying the other was bad... (3, 9).
%- When one child wrote u differently to the other, they didn't discuss :(

How the child's perception of the robot as a learning agent may change over the 
long-term remains to be seen. On one occasion during the preliminary studies, a 
child's response to whether the {\sc nao} could write its own name included that it 
may have problems with the `n', as the child had been correcting the robot on this 
letter. This suggests that users may project human-like learning features, such as 
forgetfulness, onto the robot, which may or may not actually be technically present 
in the learning agent. This may need to be capitalised on when considering how to 
extend the interaction for the long-term, as the present system with a learning rate 
such that progress is evident to the user will cause convergence for a letter within a 
few iterations.

@@

With some of the challenges towards an engaging long-term handwriting intervention 
with the teachable robotic partner addressed, further steps can be made towards 
answering the ultimate question of what impact to the outcomes of interventions the 
addition of such a teachable robotic agent would have, including with respect to the 
participants' self-esteem, motivation, or learning gains. % does it impact the
%motivation of the participants, their self-esteem, and/or the learning gains
%that they experience? We are currently considering running a long-term study
%that would provide better evidences to answer these questions.

@@

The strong social impact of early school problems makes research in this field
a certainly useful challenge for HRI.

>>>>

This article presents the first known robotic partner which children can teach handwriting. It is
hypothesised that such a system could not just engage an unmotivated student,
but could also present the opportunity for children to experience the typical
benefits encountered during human-led handwriting interventions, such as motor
mimicry. Moreover, this system allows for exploring the potential for the
\emph{learning by teaching} paradigm to be employed in the interaction, so as to
stimulate meta-cognition, empathy and increased self-esteem in the child user.

@@

If there is correlation between the points in the observations, there will be
eigenvalues of the covariance matrix which are close to zero. As such, removing
the associated eigenvectors from ${\bf \Phi}$ allows for dimensionality
reduction with minimal impact. 
%Indeed, the amount of variance in the dataset
%that is explained by each eigenvector ${\bf v}_i$ is $\sqrt{\lambda_i}$, and
%therefore the proportion of the variance explained by each dimension/eigenvector
%is as shown in (\ref{eq:proportionVar}).
%
%\begin{equation}\label{eq:proportionVar}
%\%var_i = \frac{\sqrt{\lambda_i}}{\sum_{i=1}^{N}\sqrt{\lambda_i}}\times 100\%
%\end{equation}

@@

Figure \ref{fig:demonstrationShapes2} illustrates the response of the system to
demonstrations from a child for the letter `s' using a learning rate of
$\alpha=1/2$.  Note that even poorly-written demonstrations allow the system to improve.

@@

\begin{figure}[thpb]
     \begin{center}
        %\subfigure{
        %    \includegraphics[width=0.4\textwidth]{figures/naoWriting1.png}
        %}%
        \subfigure{
            \includegraphics[width=0.6\linewidth]{figures/naoWriting2.png}
        }%
%
    \end{center}
    \caption{A demonstration of the robot simulating the writing of a word with
    its finger. The motion of the robot is synchronised with the display of the
    tablet, communicating over ROS.\protect\footnotemark}%

@@

A conclusion drawn in~\cite{Hoy2011} is that any 
handwriting intervention studies considered in the systematic review which involved 
fewer than two practice sessions per week and fewer than a total of 20 practice 
sessions, including homework, were not found to demonstrate effective results. This 
highlights the necessity to engage students in an interaction which will be sustainable
 over the long-term if we wish to move towards using the proposed system to answer 
research questions which involve the measurement of learning gains to gauge effectiveness. 
Several challenges are raised in developing such long-term capabilities for the system,
 from both technical and socialogical points of view. %not sure this makes sense

@@

In the current system, the robot can ask questions and prompt participants, but it 
cannot engage in discussions with the participants. It is clear that work is necessary 
to develop the conversational agent in the interaction so that the presence of an 
experimenter is not required for a captivating engagement. While there is the 
possiblity to focus the interaction design on group-based interaction with the robot 
in order to alleviate the necessity of a conversational agent, there is reason to 
believe that constructing such a social interaction is not a trivial task. Anectodes 
from the preliminary studies have shown that some children may criticise another's 
demonstrations to the robot, which may or may not be as damaging to a child's 
self-efficacy as when they are criticised in a typical educational context. In addition,
on occassions where a pair of children came to teach the robot different styles of a 
particular letter, they did not discuss with each other their different writing styles 
and the effect on the teaching efficiency. This may suggest that a social context in 
which verbalising opinions about differences is encouraged is necessary to get children 
to cooperate in teaching the robot.  
%- "Would have problems with the 'n'" - (8) projecting human learning characteristics.
%- awkward silence, speaking over the top of the robot to talk to experimenter....
%- Children saying the other was bad... (3, 9).
%- When one child wrote u differently to the other, they didn't discuss :(

How the children's perception of the robot as a learning agent may change over the 
long-term remains to be seen. On one occasion during the preliminary studies, a 
child's response to whether or not the {\sc nao} could write its own name included that it 
may have problems with the `n', as the child had been correcting the robot on this 
letter. This suggests that users may project human-like learning features, such as 
forgetfulness, onto the robot, which may or may not actually be technically present 
in the learning agent. This may need to be capitalised on when considering how to 
extend the interaction for long time frames, as the present system -- with a learning rate 
such that progress is evident to the user -- will cause convergence for a letter within a 
few iterations.

@@

With some of the challenges towards an engaging long-term handwriting intervention 
with the teachable robotic partner addressed, further steps can be made towards 
answering the ultimate question of what impact to the outcomes of interventions the 
addition of such a teachable robotic agent would have, including the effect on the 
participants' self-esteem, motivation, or learning gains. % does it impact the
%motivation of the participants, their self-esteem, and/or the learning gains
%that they experience? We are currently considering running a long-term study
%that would provide better evidences to answer these questions.

@@

The strong social impact of early educational problems makes research in this field
an undoubtably meaningful challenge for HRI.
